\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2021-11-19 doc/USER_MANUAL/02_getting_started.tex
minor edit
Buildbot ran the code beautifier.
updates doc

>>>>

Beware that some cluster systems that run a recent version may not run and\slash compile an older version of the code. \\

When using dynamic fault in parallel with the developer version, we suggest you to set the configuration parameters
of \texttt{FAULT\_DISPL\_VELOC} and \texttt{FAULT\_SYNCHRONIZE\_ACCEL} as \texttt{.true.}.\\

### 2021-11-19 doc/USER_MANUAL/06_fault_sources.tex
updates doc

The mesh generated in CUBIT needs to be processed and exported in
a format compatible with SPECFEM3D. This is achieved in the Python
scripts by calling the Python-CUBIT interface functions defined in
the CUBIT directory:
\begin{enumerate}
\item Function $\mathtt{define\_bc}$ (or $\mathtt{boundary\_definition.py}$)
must be called to set up the absorbing boundaries database
\item Function $\mathtt{fault\_input}$ must be called once for each fault
to set up the fault database
\item Function $\mathtt{cubit2specfem3d.export2SPECFEM3D}$ must be called
at the very end of the script to export the mesh in a SPECFEM3D format.
\end{enumerate}
The functions in \#1 and \#3 are for the bulk and are documented in
Section \ref{subsec:Exporting-the-Mesh}. We focus here on \#2:
\begin{description}
\item [{Function:}] $\mathtt{fault\_input}$
\item [{Purpose:}] export a fault mesh database from CUBIT to a SPECFEM3D-compliant
file
\item [{Syntax:}] fault\_input(id\_fault, ids\_surf\_1, ids\_surf\_2)
\item [{Inputs:}]~\end{description}
\begin{itemize}
\item id\_fault integer index assigned to the fault. (The user must number
all the faults, starting at 1, with unit increments)
\item ids\_surf\_1 list of CUBIT ids of all surfaces that form side 1 of
the fault.
\item ids\_surf\_2 list of CUBIT ids of all surfaces that form side 2 of
the fault. (The user must decide which side of the fault is side 1.
This choice affects the sign conventions of fault quantities as explained
in Section \ref{sec:Sign-Convention-for}).\end{itemize}
\begin{description}
\item [{Outputs:}] file $\mathtt{fault\_file\_X.dat}$, where X is the
fault id (id\_fault).
\item [{Example:}] For the example in Section \ref{sec:Mesh-Generation-with}:
\begin{verbatim}
  A1 = [168]
  A2 = [160]
  fault_input(1,A1,A2)
\end{verbatim}
\end{description}

@@

The rest of this file is made of namelist input blocks (see \textquotedbl{}namelist\textquotedbl{}
in a Fortran 9x manual). The input for each fault has the following
sequence (arguments in {[}brackets{]} are optional):

\&\textbf{RUPTURE\_SWITCHES}  /
RATE\_AND\_STATE ,TPV16 ,HETE\_RSF ,TPV10X ,TWF

\&\textbf{BEGIN\_FAULT} /

\&\textbf{STRESS\_TENSOR} Sigma = $\sigma_{xx}$,$\sigma_{yy}$,$\sigma_{zz}$,$\sigma_{xy}$,$\sigma_{xz}$,$\sigma_{yz}$ /

\&\textbf{INIT\_STRESS} S1, S2, S3 {[},n1, n2, n3{]} /

followed by (n1+n2+n3) \&\textbf{DIST2D} blocks

\&\textbf{SWF} mus, mud, dc {[}, nmus, nmud, ndc{]} (weakening_kind=1 for linear (default); weakening_kind=2 for exponential)/

\&\textbf{TWF} nuc\_x, nuc\_y, nuc\_z, nuc\_r, nuc\_t0, nuc\_v /

\&\textbf{RSF} V0,f0,a,b,L,V\_init,theta\_init,C,StateLaw {[} nV0,nf0,na,nb,nL,nV\_init,ntheta\_init,nC {]} /

@@

\item [{\&\textbf{SWF}}] input block sets the slip-weakening friction parameters
of the fault:
\begin{description}
\item [{mus}] = constant background value of static friction coefficient
\item [{mud}] = constant background value of dynamic friction coefficient
\item [{dc}] = constant background value of critical slip-weakening distance
\item [{C}] = constant background value of cohesion (in Pa)
\item [{nmus}] = number of heterogeneous items for static friction coefficient
{[}default is 0{]}
\item [{nmud}] = number of heterogeneous items for dynamic friction coefficient
{[}default is 0{]}
\item [{ndc}] = number of heterogeneous items for critical slip-weakening
distance {[}default is 0{]}
\item [{nC}] = number of heterogeneous items for cohesion
\item [{weakening_kind}] = 1 for linear slip-weakening law (default); 2 for exponential slip-weakening law: $\mu_d + (\mu_s-\mu_d) \exp(-\frac{u}{d_c})$
\end{description}

>>>>

The mesh generated in CUBIT needs to be processed and exported in
a format compatible with SPECFEM3D. This is achieved in the Python
scripts by calling the Python-CUBIT interface functions defined in
the CUBIT directory:
\begin{enumerate}
\item Function $\mathtt{define\_bc}$ (or $\mathtt{boundary\_definition.py}$)
must be called to set up the absorbing boundaries database
\item Function $\mathtt{fault\_input}$ must be called once for each fault
to set up the fault database
\item Function $\mathtt{cubit2specfem3d.export2SPECFEM3D}$ must be called
at the very end of the script to export the mesh in a SPECFEM3D format.
\end{enumerate}
The functions in \#1 and \#3 are for the bulk and are documented in
Section \ref{subsec:Exporting-the-Mesh}. We focus here on \#2:
\begin{description}
\item [{Function:}] $\mathtt{fault\_input}$
\item [{Purpose:}] export a fault mesh database from CUBIT to a SPECFEM3D-compliant
file
\item [{Syntax:}] fault\_input(id\_fault, ids\_surf\_1, ids\_surf\_2)
\item [{Inputs:}]~\end{description}
\begin{itemize}
\item id\_fault integer index assigned to the fault. (The user must number
all the faults, starting at 1, with unit increments)
\item ids\_surf\_1 list of CUBIT ids of all surfaces that form side 1 of
the fault.
\item ids\_surf\_2 list of CUBIT ids of all surfaces that form side 2 of
the fault. (The user must decide which side of the fault is side 1.
This choice affects the sign conventions of fault quantities as explained
in Section \ref{sec:Sign-Convention-for}).\end{itemize}
\begin{description}
\item [{Outputs:}] file $\mathtt{fault\_file\_X.dat}$, where X is the
fault id (id\_fault).
\item [{Example:}] For the example in Section \ref{sec:Mesh-Generation-with}:
{\footnotesize
\begin{verbatim}
  A1 = [168]
  A2 = [160]
  fault_input(1,A1,A2)
\end{verbatim}}
\end{description}

@@

The rest of this file is made of namelist input blocks (see \textquotedbl{}namelist\textquotedbl{}
in a Fortran 9x manual). The input for each fault has the following
sequence (arguments in {[}brackets{]} are optional):\\

\&\textbf{RUPTURE\_SWITCHES}  / RATE\_AND\_STATE ,TPV16 ,HETE\_RSF ,TPV10X ,TWF\\
\&\textbf{BEGIN\_FAULT} /\\
\&\textbf{STRESS\_TENSOR} Sigma = $\sigma_{xx}$,$\sigma_{yy}$,$\sigma_{zz}$,$\sigma_{xy}$,$\sigma_{xz}$,$\sigma_{yz}$ /\\
\&\textbf{INIT\_STRESS} S1, S2, S3 {[},n1, n2, n3{]} /\\

followed by (n1+n2+n3) \&\textbf{DIST2D} blocks\\

\&\textbf{SWF} mus, mud, dc {[}, nmus, nmud, ndc{]} (weakening\_kind=1 for linear (default); weakening\_kind=2 for exponential) /\\
\&\textbf{TWF} nuc\_x, nuc\_y, nuc\_z, nuc\_r, nuc\_t0, nuc\_v /\\
\&\textbf{RSF} V0,f0,a,b,L,V\_init,theta\_init,C,StateLaw {[} nV0,nf0,na,nb,nL,nV\_init,ntheta\_init,nC {]} /\\

@@

\item [{\&\textbf{SWF}}] input block sets the slip-weakening friction parameters
of the fault:
\begin{description}
\item [{mus}] = constant background value of static friction coefficient
\item [{mud}] = constant background value of dynamic friction coefficient
\item [{dc}] = constant background value of critical slip-weakening distance
\item [{C}] = constant background value of cohesion (in Pa)
\item [{nmus}] = number of heterogeneous items for static friction coefficient
{[}default is 0{]}
\item [{nmud}] = number of heterogeneous items for dynamic friction coefficient
{[}default is 0{]}
\item [{ndc}] = number of heterogeneous items for critical slip-weakening
distance {[}default is 0{]}
\item [{nC}] = number of heterogeneous items for cohesion
\item [{weakening\_kind}] = 1 for linear slip-weakening law (default); 2 for exponential slip-weakening law:
                            $$\mu = \mu_d + (\mu_s-\mu_d) exp(-\frac{u}{d_c}) $$
\end{description}
